Verifying Demonstrations

### 2018-08-28 paper/adversary-model.tex
Improves identity--location adversary

\begin{definition}[Base identity--location adversary]%
  \label{base-identity-location-adversary}
  The adversary controls \(S\).
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{W,P}(W, l)\) and \(d_{W,P}(P,l)\) and the 
  time it took place, \(t_{P,W}\).
  \begin{description}
    \item[The witness case:]
      The witness later communicates with \(S\), where \(S\) only learns 
      \(f(d_{W,P}(W, l))\), for some function \(f\), and the time it happened, 
      \(t_{W,S}\).
      The adversary wins if he can link \(W\) and \(l\).
    \item[The protester case:]
      The protester later communicates with \(S\), where \(S\) only learns 
      \(g(d_{W,P}(P, l))\), for some function \(g\), and the time it happened, 
      \(t_{P,S}\).
      The adversary wins if he can link \(P\) and \(l\).
  \end{description}
\end{definition}

@@

\begin{figure}
  \centering
  \includegraphics{base-identity-location-adversary.tikz}
  \caption{\label{fig:identity-location-adversary}%
    An overview of the base identity--location adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(W, l)\), and 
    the time it happened, \(t_{P,W}\).
    The witness submits \(f(d_{P,W}(W))\), for some function \(f\), and the 
    protester submits \(g(d_{P,W}(P,l))\), for some function \(g\), to the 
    storage \(S\), who learns only that and the time it happened, \(t_{W,S}\) 
    respectively \(t_{P,S}\).
    Only the storage \(S\) is controlled by the adversary \(A\).
  }
\end{figure}

>>>>

\begin{definition}[Base identity--location adversary]%
  \label{base-identity-location-adversary}
  The adversary controls \(S\).
  The witness \(W\) and the protester \(P\) communicate.
  They learn some protocol data \(d_{P,W}(P, W, l)\) and the time it took 
  place, \(t_{P,W}\).
  \begin{description}
    \item[The witness case:]
      The witness later communicates with \(S\), where \(S\) only learns 
      \(f(d_{P,W}(P, W, l))\), for some function \(f\), and the time it 
      happened, \(t_{W,S}\).
      The adversary wins if he can link \(W\) and \(l\).
    \item[The protester case:]
      The protester later communicates with \(S\), where \(S\) only learns 
      \(g(d_{P,W}(P, W, l))\), for some function \(g\), and the time it 
      happened, \(t_{P,S}\).
      The adversary wins if he can link \(P\) and \(l\).
  \end{description}
\end{definition}

@@

\begin{figure}
  \centering
  \includegraphics{base-identity-location-adversary.tikz}
  \caption{\label{fig:identity-location-adversary}%
    An overview of the base identity--location adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(P, W, l)\), 
    and the time it happened, \(t_{P,W}\).
    The witness submits \(f(d_{P,W}(P, W, l))\), for some function \(f\), and 
    the protester submits \(g(d_{P,W}(P, W, l))\), for some function \(g\), to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{W,S}\) respectively \(t_{P,S}\).
    Only the storage \(S\) is controlled by the adversary \(A\).
  }
\end{figure}
